Linear Stochastic Approximation- Constant Step-Size and Iterate Averaging

### 2017-05-19 instance.tex
updated experiments

%\vspace*{0.5em}
%\subsection{Result Discussion}
%\begin{itemize}[leftmargin=*, before = \leavevmode\vspace{-\baselineskip}]
\textbf{Role of $U$}: When the given problem $P$ is positive definite, it is straightforward to produce an $\alpha_P>0$ such that $\rhos{P}>0$ and $\rhod{P}>0,\,\forall \alpha\in(0,\alpha_P)$ by considering the definitions of $\rhos{P}$ and $\rhod{P}$. 
However, the problem $P$ being Hurwitz does not guarantee positive definiteness. % (see \Cref{ex:pdas}). 
\todoc{I commented out the examples.}
Following  \cite{lihong}, we remedy this 
by applying a similarity transformation using an appropriate $U$ that transforms a Hurwitz problem $P$ to a positive definite problem $P_U$. This can be done because any Hurwitz matrix is similar to a PD matrix. 
Taking $U$ to be this similarity matrix, we transform  \eqref{conststep} by premultiplying it by $U^{-1}$ and introducing a new variable $\gamma_t\eqdef U^{-1 }\theta_t$.
\if0
To see how this works, let $\gamma_t\eqdef U^{-1 }\theta_t$. Premultiplying 
 \eqref{conststep} by $U^{-1}$ and plugging in $\gamma_t$, we get
\begin{align*}
%U^{-1}\theta_t&=U^{-1}\theta_{t-1}+\alpha(U^{-1} b_t- U^{-1}A_t U U^{-1}\theta_{t-1}),\\
\gamma_t&=\gamma_{t-1}+\alpha(U^{-1} b_t- J_t\gamma_{t-1}),
\end{align*}
where $J_t = U^{-1}A_t U$.
Now, since any Hurwitz matrix is similar to a PD matrix with an appropriate similarity transformation $U$, choosing $U$ this way we get that $\E[J_t]$ is PD, hence $P_U$ is PD.
\fi
%This completes the transformation of a Hurwitz problem $P$ to a positive definite problem $P_U$. 
The condition number $\cond{U}$ appears in our bound because $\theta_t$ is recovered from $\gamma_t$ using
$\theta_t=U\gamma_t$. Of course, when the problem $P$ is positive definite, we can let $U=\I$ in \Cref{th:rate}. 
More generally, one can always take $U$ in the result that leads to the smallest bound.

\textbf{Role of $\rhos{P}$ and $\rhod{P}$}: 
When $P$ is positive definite, we can expand the MSE as 
\begin{align}
\label{eq:exp}
	\EE{\norm{\eh_t}^2}=\tfrac{1}{(t+1)^2}\, \ip{ \textstyle\sum_{s=0}^t e_s,\textstyle\sum_{s=0}^t e_s}\,,
\end{align} 
where $\eh_t = \thh_t-\ts$ and $e_t = \theta_t-\ts$.
The inner product in \eqref{eq:exp} is a summation of \emph{diagonal} terms $\EE{\ip{e_s,e_s}}$ and \emph{cross} terms of $\EE{\ip{e_s,e_q}}$, $s\neq q$. The growth of the diagonal terms and the cross terms depends on the spectral norm of the random matrices $H_t=I-\alpha A_t$ and that of the deterministic matrix $H_P=I-\alpha A_P$, respectively. These are given by
\begin{comment}
The output $\thh_t$ of the algorithm \eqref{eq:lsa} is the average of the internal states at times $s=0,\ldots,t-1$. The error dynamics of the internal states by looking at the behavior of $e_t\eqdef \theta_t-\ts$.
\begin{align}\label{eq:errec}
\theta_t&=\theta_{t-1}+\alpha(b_t-A_t\theta_{t-1})\nn\\
\theta_t-\ts&=\theta_{t-1}-\ts+\alpha\left(b_t-A_t(\theta_{t-1}-\ts+\ts)\right)\nn\\
e_t&=e_{t-1}+\alpha(b_t-A_t e_t -A_t\ts)\nn\\
e_t&=\underbrace{((I-\alpha A_t))}_{\text{Random-Matrix}} e_{t-1}+\underbrace{\alpha(N_t -(M_t)\ts)}_{\text{Noise}}
\end{align}
From \eqref{errec} it is clear that the error dynamics depends on the $i)$ properties of the random matrix, $ii)$ properties of the noise. In the absence of the noise term in \eqref{eq:errec}, we have $e_t=(I-\alpha A_t) e_{t-1}=\Pi_{s=1}(I-\alpha A_s) e_0$, i.e., the initial error is get multiplied by a product of random matrices. In such a scenario, we can guess that whether or not the algorithm forgets the bias $\norm{\theta_0-\ts}$, depends on whether the matrix product is contracting. One way to characterize this contracting property is to look at the spectral radius of the random matrix, which is given by
\end{comment}
\begin{align}\label{eq:spectralrand}
\EE{\norm{I-\alpha A_t}^2}=1-\alpha \rhos{P}, \quad  {\norm{I-\alpha A_P}^2}=1-\alpha \rhod{P}\,,
\end{align}
justifying the appearance of $\rhos{P}$ and $\rhod{P}$.
%Note that \eqref{eq:spectralrand} explicitly connects $\rhod{P}$ and $\rhos{P}$ in \Cref{def:dist} to the spectral norms matrices $H_t$ and $H_P$. 
For the MSE to be bounded, we need the spectral norms to be less than unity, implying the conditions $\rhos{P}>0$ and $\rhod{P}>0$. If $P$ is Hurwitz, we can argue on similar lines by first transforming $P$ into a positive definite problem $P_U$ and replacing $\rhos{P}$ and $\rhod{P}$ by $\rhos{P_U}$ and $\rhod{P_U}$, and introducing $\cond{U}$ to account for the forward ($\gamma=U^{-1}\theta$) and reverse ($\theta=U\gamma$) transformations using $U^{-1}$ and $U$ respectively.

>>>>

%\vspace*{0.5em}
%\subsection{Result Discussion}
%\begin{itemize}[leftmargin=*, before = \leavevmode\vspace{-\baselineskip}]
\textbf{Role of $U$}: $U$ is helpful in transforming the recursion in $\theta_t$ to $\gamma_t=U^{-1}\theta_t$, which helps in ensuring $\rhos{P_U}>0$. Such similarity transformation have also been considered in analysis of RL algorithms \cite{lihong}. The condition number $\cond{U}$ appears in our bound because $\theta_t$ is recovered from $\gamma_t$ using
$\theta_t=U\gamma_t$. Of course, when the problem $P$ is positive definite, we can let $U=\I$ in \Cref{th:rate}.
More generally, one can always take $U$ in the result that leads to the smallest bound.
\begin{comment}
\textbf{Role of $U$}: When the given problem $P$ is positive definite, it is straightforward to produce an $\alpha_P>0$ such that $\rhos{P}>0$ and $\rhod{P}>0,\,\forall \alpha\in(0,\alpha_P)$ by considering the definitions of $\rhos{P}$ and $\rhod{P}$.
However, the problem $P$ being Hurwitz does not guarantee positive definiteness. % (see \Cref{ex:pdas}). 
\todoc{I commented out the examples.}
Following  \cite{lihong}, we remedy this 
by applying a similarity transformation using an appropriate $U$ that transforms a Hurwitz problem $P$ to a positive definite problem $P_U$. This can be done because any Hurwitz matrix is similar to a PD matrix. 
Taking $U$ to be this similarity matrix, we transform  \eqref{conststep} by premultiplying it by $U^{-1}$ and introducing a new variable $\gamma_t\eqdef U^{-1 }\theta_t$.
\if0
To see how this works, let $\gamma_t\eqdef U^{-1 }\theta_t$. Premultiplying 
 \eqref{conststep} by $U^{-1}$ and plugging in $\gamma_t$, we get
\begin{align*}
%U^{-1}\theta_t&=U^{-1}\theta_{t-1}+\alpha(U^{-1} b_t- U^{-1}A_t U U^{-1}\theta_{t-1}),\\
\gamma_t&=\gamma_{t-1}+\alpha(U^{-1} b_t- J_t\gamma_{t-1}),
\end{align*}
where $J_t = U^{-1}A_t U$.
Now, since any Hurwitz matrix is similar to a PD matrix with an appropriate similarity transformation $U$, choosing $U$ this way we get that $\E[J_t]$ is PD, hence $P_U$ is PD.
\fi
%This completes the transformation of a Hurwitz problem $P$ to a positive definite problem $P_U$. 
The condition number $\cond{U}$ appears in our bound because $\theta_t$ is recovered from $\gamma_t$ using
$\theta_t=U\gamma_t$. Of course, when the problem $P$ is positive definite, we can let $U=\I$ in \Cref{th:rate}. 
More generally, one can always take $U$ in the result that leads to the smallest bound.
\end{comment}
\textbf{Role of $\rhos{P}$ and $\rhod{P}$}: 
When $P$ is positive definite, we can expand the MSE as 
\begin{align}
\label{eq:exp}
	\EE{\norm{\eh_t}^2}=\tfrac{1}{(t+1)^2}\, \ip{ \textstyle\sum_{s=0}^t e_s,\textstyle\sum_{s=0}^t e_s}\,,
\end{align} 
where $\eh_t = \thh_t-\ts$ and $e_t = \theta_t-\ts$.
The inner product in \eqref{eq:exp} is a summation of \emph{diagonal} terms $\EE{\ip{e_s,e_s}}$ and \emph{cross} terms of $\EE{\ip{e_s,e_q}}$, $s\neq q$. The growth of the diagonal terms and the cross terms depends on the spectral norm of the random matrices $H_t=I-\alpha A_t$ and that of the deterministic matrix $H_P=I-\alpha A_P$, respectively. These are given by
\begin{comment}
The output $\thh_t$ of the algorithm \eqref{eq:lsa} is the average of the internal states at times $s=0,\ldots,t-1$. The error dynamics of the internal states by looking at the behavior of $e_t\eqdef \theta_t-\ts$.
\begin{align}\label{eq:errec}
\theta_t&=\theta_{t-1}+\alpha(b_t-A_t\theta_{t-1})\nn\\
\theta_t-\ts&=\theta_{t-1}-\ts+\alpha\left(b_t-A_t(\theta_{t-1}-\ts+\ts)\right)\nn\\
e_t&=e_{t-1}+\alpha(b_t-A_t e_t -A_t\ts)\nn\\
e_t&=\underbrace{((I-\alpha A_t))}_{\text{Random-Matrix}} e_{t-1}+\underbrace{\alpha(N_t -(M_t)\ts)}_{\text{Noise}}
\end{align}
From \eqref{errec} it is clear that the error dynamics depends on the $i)$ properties of the random matrix, $ii)$ properties of the noise. In the absence of the noise term in \eqref{eq:errec}, we have $e_t=(I-\alpha A_t) e_{t-1}=\Pi_{s=1}(I-\alpha A_s) e_0$, i.e., the initial error is get multiplied by a product of random matrices. In such a scenario, we can guess that whether or not the algorithm forgets the bias $\norm{\theta_0-\ts}$, depends on whether the matrix product is contracting. One way to characterize this contracting property is to look at the spectral radius of the random matrix, which is given by
\end{comment}
\begin{align}\label{eq:spectralrand}
\EE{\norm{I-\alpha A_t}^2}=1-\alpha \rhos{P}, \quad  {\norm{I-\alpha A_P}^2}=1-\alpha \rhod{P}\,,
\end{align}
justifying the appearance of $\rhos{P}$ and $\rhod{P}$.
%Note that \eqref{eq:spectralrand} explicitly connects $\rhod{P}$ and $\rhos{P}$ in \Cref{def:dist} to the spectral norms matrices $H_t$ and $H_P$. 
For the MSE to be bounded, we need the spectral norms to be less than unity, implying the conditions $\rhos{P}>0$ and $\rhod{P}>0$. If $P$ is Hurwitz, we can argue on similar lines by first transforming $P$ into a positive definite problem $P_U$ and replacing $\rhos{P}$ and $\rhod{P}$ by $\rhos{P_U}$ and $\rhod{P_U}$, and introducing $\cond{U}$ to account for the forward ($\gamma=U^{-1}\theta$) and reverse ($\theta=U\gamma$) transformations using $U^{-1}$ and $U$ respectively.

### 2017-05-19 intro.tex
updated experiments

In this paper, we study LSAs with CS-PR (thereby extending prior work by \citet{bach} from SGD to general LSAs) \todoc{Do our results imply theirs? Do we simplify improve their bounds, while extending the scope? Even if the answer is no, we need to add remarks on these questions.}
in an effort to understand the effectiveness of the CS-PR technique beyond SGD.
Of particular interest is whether a similar result to that  \citet{bach} holds
for the TD class of LSA algorithms used in RL.
For simplicity, we still consider the \iid case. Our restrictions on the common distribution is that the ``noise variance'' should be bounded (as we consider squared errors), and that the matrix $\E[A_t]$ must be Hurwitz, i.e., all its eigenvalues have positive real parts. This latter assumption can be shown to be necessary for the stability of the LSA iterations. \todoc{Add citation. Or remove/comment out the sentence.}
One setting that fits our assumption is \emph{policy evaluation} \cite{dann} using linear value function approximation from experience replay \cite{lin} in a batch setting \cite{lange} in RL using the TD class of algorithms \cite{sutton,konda-tsitsiklis,gtd,gtd2,gtdmp}.

@@

where no constant step-size is available to prevent exploding MSE. Further, it is empirically demonstrated that the method is able to find a step-size, which is close to the theoretically recommended stepsize which results in the fastest convergence. \todoc{True??}

@@

In addition to TD($0$), our results directly can be applied to a host of \emph{off-policy} TD algorithms such as GTD/GTD2/TDC with CS-PR. \todoc{How about TD($\lambda$)? Will we discuss this somewhere? Maybe in the organization section this can be mentioned.}
In the case of TDC only asymptotic bounds were known \cite{gtd2} and our results are a first step 
\todoc{Why only a step? What is missing?} towards proving finite time bounds. Also, our results show that the GTD class of algorithms guarantee a $O(\frac{1}{t})$ rate for MSE (without use of projections), improving on a previous result by \citet{gtdmp} that guaranteed a $O(\frac{1}{\sqrt{t}})$ rate for this class for the projected version of the algorithm. \todoc{And projections are problematic on their own. Will we discuss this somewhere. Or should the projection issue be a footnote here?}

@@

\paragraph{Organization:} The paper is organized as follows \todoc{Do not forget to fill this in.}

>>>>

In this paper, we study LSAs with CS-PR (thereby extending prior work by \citet{bach} from SGD to general LSAs) \todoc{Do our results imply theirs? Do we simplify improve their bounds, while extending the scope? Even if the answer is no, we need to add remarks on these questions.}
in an effort to understand the effectiveness of the CS-PR technique beyond SGD.
Of particular interest is whether a similar result to that  \citet{bach} holds
for the TD class of LSA algorithms used in RL.
For simplicity, we still consider the \iid case. Our restrictions on the common distribution is that the ``noise variance'' should be bounded (as we consider squared errors), and that the matrix $\E[A_t]$ must be Hurwitz, i.e., all its eigenvalues have positive real parts. %This latter assumption can be shown to be necessary for the stability of the LSA iterations. \todoc{Add citation. Or remove/comment out the sentence.}
One setting that fits our assumption is \emph{policy evaluation} \cite{dann} using linear value function approximation from experience replay \cite{lin} in a batch setting \cite{lange} in RL using the TD class of algorithms \cite{sutton,konda-tsitsiklis,gtd,gtd2,gtdmp}.

@@

where no constant step-size is available to prevent exploding MSE. %Further, it is empirically demonstrated that the method is able to find a step-size, which is close to the theoretically recommended stepsize which results in the fastest convergence. \todoc{True??}

@@

In addition to TD($0$), our results directly can be applied to other \emph{off-policy} TD algorithms such as GTD/GTD2 with CS-PR. \todoc{How about TD($\lambda$)? Will we discuss this somewhere? Maybe in the organization section this can be mentioned.}
%In the case of TDC only asymptotic bounds were known \cite{gtd2} and our results are a first step
%\todoc{Why only a step? What is missing?} towards proving finite time bounds.
In particular, our results show that the GTD class of algorithms guarantee a $O(\frac{1}{t})$ rate for MSE (without use of projections), improving on a previous result by \citet{gtdmp} that guaranteed a $O(\frac{1}{\sqrt{t}})$ rate for this class for the projected version of the algorithm. \todoc{And projections are problematic on their own. Will we discuss this somewhere. Or should the projection issue be a footnote here?}

@@

%\paragraph{Organization:} The paper is organized as follows \todoc{Do not forget to fill this in.}

### 2017-05-19 related.tex
updated experiments

\textbf{Results for RL}: We are presented with data in the form of an \iid sequence $(\phi_t,\phi'_t,r_t)\in \R^d\times\R^d\times \R$. For a fixed constant $\gamma \in (0,1)$ define  $\Delta_t\eqdef \phi_t\phi_t^\top-\gamma \phi_t\phi_t^{'\top}$, $C_t=\phi_t\phi_t^\top$ and $b_t=\phi_r r_t$. In what follows, $\mu_t>0$ is an \emph{importance} sampling factor whose aim is to correct for mismatch in the (behavior) distribution with which the data was collected and the (target) distribution with respect to which one wants to learn. A factor $\mu_t=1,\,\forall t\geq 0$ will mean that no correction is required\footnote{This is known as the \emph{on-policy} case where the behavior is identical to the target. The general setting where $\mu_t>0$ is known as \emph{off-policy}.}. The various TD class of algorithms that can be cast as LSAs are given in \cref{tb:tdalgo}.
\FloatBarrier
\begin{table}[h]
\resizebox{\columnwidth}{!}{
\begin{tabular}{|c|l|p{60mm}|}\hline
Algorithm& Update & Remark\\ \hline
TD(0) 
	& $\begin{aligned}\theta_t&=\theta_{t-1}+\alpha_t (b_t -\Delta_t\theta_{t-1})\end{aligned}$ 
	& \cite{korda-prashanth}: $\alpha_t=O(\frac{1}{t})^\beta$, $\beta\in(0,1)$; PR-avg, ``on-policy''; $\EE{\norm{\eh_t}}= O(\frac{1}{\sqrt{t}}).$ \\ \hline
GTD/GTD2
	& $\begin{aligned} y_{t}&=y_{t-1}+\beta_t(\mu_t b_t -\mu_t \Delta_t \theta_{t-1}- Q_t y_{t-1})\\ \theta_t &=\theta_{t-1}+\alpha_t (\mu_t A^\top_t y_{t-1})\end{aligned}$
	& \cite{gtd2}: $\beta_t=\eta \alpha_t$, $\sum_{t\geq 0}\alpha_t=\infty$, $\sum_{t\geq 0}\alpha^2_t<\infty$; $e_t\ra 0$ as $t\ra\infty$ w.p.1. 
	\cite{gtdmp}: $\alpha_t=\beta_t=O(\frac{1}{\sqrt{t}})$; Projection+PR; $\,\norm{e_t} =O(t^{-\frac{1}{4}})$ w.h.p.\\\hline
TDC
	& $\begin{aligned} y_{t}&=y_{t-1}+\beta_t(\mu_t b_t -\mu_t \Delta_t \theta_{t-1}-C_t y_{t-1})\\ \theta_t &=\theta_{t-1}+\alpha_t (\mu_t b_t-\mu_t\Delta_t\theta_{t-1}+ (\Delta^\top_t-C_t)y_{t-1})\end{aligned}$ 
	& \cite{gtd2}: $\beta_t=\eta \alpha_t$, $\sum_{t\geq 0}\alpha_t=\infty$, $\sum_{t\geq 0}\alpha^2_t<\infty$; $e_t\ra 0$ as $t\ra\infty$ w.p.1. \\\hline
\end{tabular}
}
\caption{Rates for TD algorithms available in the literature \cite{korda-prashanth,gtdmp,gtd2}. }
\label{tb:tdalgo}
\end{table}
\begin{comment}
\begin{table}
\resizebox{\columnwidth}{!}{
\begin{tabular}{|c|c|c|c|c|}\hline
Algorithm& Update &Stepsize &Rate \\ \hline
TD(0)& $\begin{aligned}\theta_t&=\theta_{t-1}+\alpha_t (b_t -\Delta_t\theta_{t-1})\\ \thh_t&=\frac{1}{t+1}\sum_{s=0}^t \theta_t\end{aligned}$ &$\begin{aligned}\alpha_t&=O(\frac1{t})^\delta,\\ &\delta\in(1/2,1)\end{aligned}$ &$\EE{\norm{\eh_t}}\leq O(\frac{1}{\sqrt{t}})$ for $\delta\ra 1$ \\ \hline
GTD& $\begin{aligned} y_{t}&=y_{t-1}+\beta_t(\mu_t b_t -\mu_t \Delta_t \theta_{t-1}- Q_t y_{t-1})\\ \theta_t &=\theta_{t-1}+\alpha_t (\mu_t A^\top_t y_{t-1})\end{aligned}$ & $\begin{aligned}&\beta_t=\eta \alpha_t,\sum_{t\geq 0}\alpha_t=\infty, \\ &\sum_{t\geq 0}\alpha^2_t<\infty \end{aligned}$ & $e_t\ra 0$ w.p.1 \\\hline
TDC& $\begin{aligned} y_{t}&=y_{t-1}+\beta_t(\mu_t b_t -\mu_t \Delta_t \theta_{t-1}-C_t y_{t-1})\\ \theta_t &=\theta_{t-1}+\alpha_t (\mu_t b_t-\mu_t\Delta_t\theta_{t-1}+ (\Delta^\top_t-C_t)y_{t-1})\end{aligned}$ & $\begin{aligned}&\beta_t,\alpha_t,\frac{\alpha_t}{\beta_t} \ra 0,~\text{as}~t\ra \infty,\\& \sum_{t\geq 0}\alpha_t=\infty, \sum_{t\geq 0}\beta_t=\infty, \\ &\sum_{t\geq 0}\alpha^2_t<\infty, \sum_{t\geq 0}\beta^2_t<\infty \end{aligned}$ & $e_t\ra 0$ w.p.1 \\\hline
GTD& $\begin{aligned} y_{t}&=\Pi_Y \left(y_{t-1}+\alpha_t(\mu_t b_t -\mu_t \Delta_t \theta_{t-1}-Q_t y_{t-1})\right)\\ \theta_t &=\Pi_{\Theta}\left(\theta_{t-1}+\alpha_t (\mu_t A_t^\top y_{t-1})\right)\\ \thh_t&=\frac{\sum_{s=0}^t \alpha_s\theta_s}{\sum_{s=0}^t \alpha_s}\end{aligned}$ & $\alpha_t =O(\frac{1}{\sqrt{t}})$ & $\norm{A_P\eh_t-b}^2 \leq O(\frac{1}{\sqrt{t}})$ w.h.p\\\hline

@@

All previous results on these RL algorithms assume that \Cref{assmp:lsa} holds (the Hurwitz assumption is satisfied by definition for on-policy TD(0), while it holds by design for the others). \todoc{Are we sure?
How about TDC? How about GTD-Mirror-Prox?}
Thus, \Cref{th:rate} applies to all of TD(0)/TDC/GTD/GTD2/GTDMP with CS-PR in all cases considered in the literature.
Finite time performance of TDC was unkown in prior literature and our work provides a first step by understanding TDC with CS-PR. \todoc{I think this could be considered a major result if the Hurwitz condition can be shown to hold.}
Further, our results show that the error in the GTD class of algorithms decay at the $O(\frac{1}{t})$ rate (even without use of projection or mirror maps) instead of $O(\frac{1}{\sqrt{t}})$, a major improvement on previously published results. In comparison to the TD(0) results by \citet{korda-prashanth}, \Cref{th:rate} is better in that it provides the bias/variance decomposition. Further, their results are specific to TD(0) where $A_P$ is known to be positive definite, and it is unclear whether it extends in a straightforward manner to the GTD class or TDC. \todoc{Would not the similarity transform idea work? Why not? A comment is needed.}
However, it is important to note that \citet{korda-prashanth} handle the Markov noise case which is not dealt with in this paper. \todoc{How about others? We should mention if others also assume iid.}
\begin{comment}
\paragraph{Related Work in RL} The various temporal difference learning algorithms can be written as in \Cref{table:td}. The TD(0) algorithm is an on-policy algorithm ($\mu_t=1$) and is unstable in the general {off-policy} setting. The gradient temporal difference (GTD) algorithm \cite{gtd,gtd2,gtdmp} is stable in off-policy setting as well. Recent work by \cite{korda-prashanth} derive finite time bounds for the TD(0) for two different cases of step-sizes one without PR averaging and other with PR averaging. In the case without PR averaging, \cite{korda-prashanth} consider step-sizes of the form $\frac{c_0c}{c+t}$, where $c_0$ and $c$ are problem dependent positive constants, to dervie a rate of $O(\frac{1}{t})$ for the MSE.  In the case with PR averaging (row $1$ of \Cref{tb:rates}), \cite{korda-prashanth} consider step-size of the from $c_0\left(\frac{c}{c+t}\right)^\delta,\,\delta \in (1/2,1)$ where $c_0, c$ are problem independent positive constants, and show that this choice yeilds a rate of $O(\frac{1}{t})$ for $\delta \ra 1$ and $t\geq t_0$ (where $t_0$ is a problem dependent time instant). A possible limiting feature of the results by \cite{korda-prashanth} is that either the problem knowledge is required or the bounds hold only after a problem dependent time. A centered TD(0) variant is also considered by \cite{korda-prashanth}, however, a projection operator is required to keep the iterates bounded. Also, the bounds by \cite{korda-prashanth} don't have an explicit bias variance decomposition. The works on GTD and TDC by \cite{gtd,gtd2} show only asymptotic convergence w.p.1. Recently, the work by \cite{gtdmp} shows a rate of $\frac{1}{\sqrt{t}}$ for GTD with use of projection operation, and also proposed a variant namely GTD-Mirror-prox based on stochastic mirror-prox ideas which achieves $\frac{1}{\sqrt{t}}$ rate without use of projection. In comparison, we don't use of projections, our bounds hold for all time $t$, and the bounds are dependent on the problem instance only to the extent of choosing a step-size that leads to stable behavior, in which case we show that $O\frac{1}{t}$ rate holds (the scaling factor hidden in the $O$ expression is problem dependent). Further, our results provide explicit bias variance decomposition.
\end{comment}

>>>>

\textbf{Results for RL}: We are presented with data in the form of an \iid sequence $(\phi_t,\phi'_t,r_t)\in \R^d\times\R^d\times \R$. For a fixed constant $\gamma \in (0,1)$ define  $\Delta_t\eqdef \phi_t\phi_t^\top-\gamma \phi_t\phi_t^{'\top}$, $C_t=\phi_t\phi_t^\top$ and $b_t=\phi_r r_t$. In what follows, $\mu_t>0$ is an \emph{importance} sampling factor whose aim is to correct for mismatch in the (behavior) distribution with which the data was collected and the (target) distribution with respect to which one wants to learn. A factor $\mu_t=1,\,\forall t\geq 0$ will mean that no correction is required\footnote{This is known as the \emph{on-policy} case where the behavior is identical to the target. The general setting where $\mu_t>0$ is known as \emph{off-policy}.}. The various TD class of algorithms that can be cast as LSAs are given in \cref{tb:tdalgo}.
\FloatBarrier
\begin{table}[h]
\resizebox{\columnwidth}{!}{
\begin{tabular}{|c|l|p{60mm}|}\hline
Algorithm& Update & Remark\\ \hline
TD(0) 
	& $\begin{aligned}\theta_t&=\theta_{t-1}+\alpha_t (b_t -\Delta_t\theta_{t-1})\end{aligned}$ 
	& \cite{korda-prashanth}: $\alpha_t=O(\frac{1}{t})^\beta$, $\beta\in(0,1)$; PR-avg, ``on-policy''; $\EE{\norm{\eh_t}}= O(\frac{1}{\sqrt{t}}).$ \\ \hline
GTD/GTD2
	& $\begin{aligned} y_{t}&=y_{t-1}+\beta_t(\mu_t b_t -\mu_t \Delta_t \theta_{t-1}- Q_t y_{t-1})\\ \theta_t &=\theta_{t-1}+\alpha_t (\mu_t A^\top_t y_{t-1})\end{aligned}$
	& \cite{gtd2}: $\beta_t=\eta \alpha_t$, $\sum_{t\geq 0}\alpha_t=\infty$, $\sum_{t\geq 0}\alpha^2_t<\infty$; $e_t\ra 0$ as $t\ra\infty$ w.p.1. 
	\cite{gtdmp}: $\alpha_t=\beta_t=O(\frac{1}{\sqrt{t}})$; Projection+PR; $\,\norm{e_t} =O(t^{-\frac{1}{4}})$ w.h.p.\\\hline
%TDC
%	& $\begin{aligned} y_{t}&=y_{t-1}+\beta_t(\mu_t b_t -\mu_t \Delta_t \theta_{t-1}-C_t y_{t-1})\\ \theta_t &=\theta_{t-1}+\alpha_t (\mu_t b_t-\mu_t\Delta_t\theta_{t-1}+ (\Delta^\top_t-C_t)y_{t-1})\end{aligned}$
	%& \cite{gtd2}: $\beta_t=\eta \alpha_t$, $\sum_{t\geq 0}\alpha_t=\infty$, $\sum_{t\geq 0}\alpha^2_t<\infty$; $e_t\ra 0$ as $t\ra\infty$ w.p.1. \\\hline
\end{tabular}
}
\caption{Rates for TD algorithms available in the literature \cite{korda-prashanth,gtdmp,gtd2}. }
\label{tb:tdalgo}
\end{table}
\begin{comment}
\begin{table}
\resizebox{\columnwidth}{!}{
\begin{tabular}{|c|c|c|c|c|}\hline
Algorithm& Update &Stepsize &Rate \\ \hline
TD(0)& $\begin{aligned}\theta_t&=\theta_{t-1}+\alpha_t (b_t -\Delta_t\theta_{t-1})\\ \thh_t&=\frac{1}{t+1}\sum_{s=0}^t \theta_t\end{aligned}$ &$\begin{aligned}\alpha_t&=O(\frac1{t})^\delta,\\ &\delta\in(1/2,1)\end{aligned}$ &$\EE{\norm{\eh_t}}\leq O(\frac{1}{\sqrt{t}})$ for $\delta\ra 1$ \\ \hline
GTD& $\begin{aligned} y_{t}&=y_{t-1}+\beta_t(\mu_t b_t -\mu_t \Delta_t \theta_{t-1}- Q_t y_{t-1})\\ \theta_t &=\theta_{t-1}+\alpha_t (\mu_t A^\top_t y_{t-1})\end{aligned}$ & $\begin{aligned}&\beta_t=\eta \alpha_t,\sum_{t\geq 0}\alpha_t=\infty, \\ &\sum_{t\geq 0}\alpha^2_t<\infty \end{aligned}$ & $e_t\ra 0$ w.p.1 \\\hline
TDC& $\begin{aligned} y_{t}&=y_{t-1}+\beta_t(\mu_t b_t -\mu_t \Delta_t \theta_{t-1}-C_t y_{t-1})\\ \theta_t &=\theta_{t-1}+\alpha_t (\mu_t b_t-\mu_t\Delta_t\theta_{t-1}+ (\Delta^\top_t-C_t)y_{t-1})\end{aligned}$ & $\begin{aligned}&\beta_t,\alpha_t,\frac{\alpha_t}{\beta_t} \ra 0,~\text{as}~t\ra \infty,\\& \sum_{t\geq 0}\alpha_t=\infty, \sum_{t\geq 0}\beta_t=\infty, \\ &\sum_{t\geq 0}\alpha^2_t<\infty, \sum_{t\geq 0}\beta^2_t<\infty \end{aligned}$ & $e_t\ra 0$ w.p.1 \\\hline
GTD& $\begin{aligned} y_{t}&=\Pi_Y \left(y_{t-1}+\alpha_t(\mu_t b_t -\mu_t \Delta_t \theta_{t-1}-Q_t y_{t-1})\right)\\ \theta_t &=\Pi_{\Theta}\left(\theta_{t-1}+\alpha_t (\mu_t A_t^\top y_{t-1})\right)\\ \thh_t&=\frac{\sum_{s=0}^t \alpha_s\theta_s}{\sum_{s=0}^t \alpha_s}\end{aligned}$ & $\alpha_t =O(\frac{1}{\sqrt{t}})$ & $\norm{A_P\eh_t-b}^2 \leq O(\frac{1}{\sqrt{t}})$ w.h.p\\\hline

@@

All previous results on these RL algorithms assume that \Cref{assmp:lsa} holds (the Hurwitz assumption is satisfied by definition for on-policy TD(0), while it holds by design for the others). \todoc{Are we sure?
How about TDC? How about GTD-Mirror-Prox?}
Thus, \Cref{th:rate} applies to all of TD(0)/GTD/GTD2/ with CS-PR in all cases considered in the literature.
%Finite time performance of TDC was unkown in prior literature and our work provides a first step by understanding TDC with CS-PR. \todoc{I think this could be considered a major result if the Hurwitz condition can be shown to hold.}
In particular, our results show that the error in the GTD class of algorithms decay at the $O(\frac{1}{t})$ rate (even without use of projection or mirror maps) instead of $O(\frac{1}{\sqrt{t}})$, a major improvement on previously published results. In comparison to the TD(0) results by \citet{korda-prashanth}, \Cref{th:rate} is better in that it provides the bias/variance decomposition. Further, their results are specific to TD(0) where $A_P$ is known to be positive definite, and it is unclear whether it extends in a straightforward manner to the GTD class or TDC. \todoc{Would not the similarity transform idea work? Why not? A comment is needed.}
However, it is important to note that \citet{korda-prashanth} handle the Markov noise case which is not dealt with in this paper. \todoc{How about others? We should mention if others also assume iid.}
\begin{comment}
\paragraph{Related Work in RL} The various temporal difference learning algorithms can be written as in \Cref{table:td}. The TD(0) algorithm is an on-policy algorithm ($\mu_t=1$) and is unstable in the general {off-policy} setting. The gradient temporal difference (GTD) algorithm \cite{gtd,gtd2,gtdmp} is stable in off-policy setting as well. Recent work by \cite{korda-prashanth} derive finite time bounds for the TD(0) for two different cases of step-sizes one without PR averaging and other with PR averaging. In the case without PR averaging, \cite{korda-prashanth} consider step-sizes of the form $\frac{c_0c}{c+t}$, where $c_0$ and $c$ are problem dependent positive constants, to dervie a rate of $O(\frac{1}{t})$ for the MSE.  In the case with PR averaging (row $1$ of \Cref{tb:rates}), \cite{korda-prashanth} consider step-size of the from $c_0\left(\frac{c}{c+t}\right)^\delta,\,\delta \in (1/2,1)$ where $c_0, c$ are problem independent positive constants, and show that this choice yeilds a rate of $O(\frac{1}{t})$ for $\delta \ra 1$ and $t\geq t_0$ (where $t_0$ is a problem dependent time instant). A possible limiting feature of the results by \cite{korda-prashanth} is that either the problem knowledge is required or the bounds hold only after a problem dependent time. A centered TD(0) variant is also considered by \cite{korda-prashanth}, however, a projection operator is required to keep the iterates bounded. Also, the bounds by \cite{korda-prashanth} don't have an explicit bias variance decomposition. The works on GTD and TDC by \cite{gtd,gtd2} show only asymptotic convergence w.p.1. Recently, the work by \cite{gtdmp} shows a rate of $\frac{1}{\sqrt{t}}$ for GTD with use of projection operation, and also proposed a variant namely GTD-Mirror-prox based on stochastic mirror-prox ideas which achieves $\frac{1}{\sqrt{t}}$ rate without use of projection. In comparison, we don't use of projections, our bounds hold for all time $t$, and the bounds are dependent on the problem instance only to the extent of choosing a step-size that leads to stable behavior, in which case we show that $O\frac{1}{t}$ rate holds (the scaling factor hidden in the $O$ expression is problem dependent). Further, our results provide explicit bias variance decomposition.
\end{comment}
